\subsection{Requirement Name}
Swift Scan, the Android and Desktop apps will be tested for performance to make sure that information storage and retrieval are executed fast when the user interacts with the GUI. The Android app, which will be used to search for brewery products using various criteria such as name , best buy date and style. It will  quickly establish connection to the database and retrieve the product information for the beverage choice of the user.  On the other hand, the destop app will allow the user to easily manage the information that is stored in the database. The desktop app is to make it feasible for the customer to use and navigate. 
\subsubsection{Description}
The applications will be written in Java and the Android app will use Anroid's API in Android Studio to develop the user interface.  The functionality of both applications will consist of using up-to-date API's for the feel-and-look of the GUI and also any data that must be stored and retrieved from the database will consist of using the MySQL commands within the code for faster performance of both applications. 
\subsubsection{Source}
Doctor Chris Conly is the source and the customer here for this project
\subsubsection{Constraints}
Due to the budget, we won't know how the Android app will respond on different smartphones running Android OS.  Furthermore, the charging port on smartphones is different for different brands and the barcode scanner that will be purchased will be used on Samsung smartphones.
Detailed description of applicable constraints...
\subsubsection{Standards}
A precise brewing inventory app with various criteria and easily accessible and a good GUI.
List of applicable standards
\subsubsection{Priority}
Priority
Search types option available such as best by date, style, name.
Able to pull up information using barcode or the name.
Should be able to customise.
