This section provides a high-level statement of your product concept - what it is intended to do and how it is intended to be used. Include in this header paragraph, a brief synopsis of what is described here. For example, this header paragraph might say something like: "This section describes the purpose, use and intended user audience for the X product. X is a system that performs Y. Users of X will be able to Z..."

\subsection{Purpose and Use}
Our app is Beer Inventory app. It promotes to manage beer items, manage transaction and search for item by order. Even, it focuses on arrangement of beer, pricing, manufacturing and expiry date.  In Beer Inventory app, we are using Scanner, android app/raspberry pie and database management system.  We are using Scanner to track and scan the beer items, and it records the items, transaction, pricing and dates in the database management system. We are using android phone to display the beer items. It will also show the beer items on the basis of search; items by order, name and date

\subsection{Intended Audience}
Our intended audience for the project is Chris Colny. We are going to check the collection of beer available with Chris Conly, with the product we designed and made (Beer inventory app). If this product will be made available in the public or commercially, then convenient stores, restaurant, brewing companies and hotels will purchase our products because they used this product quite often in their daily used while managing beer, storing price, date and for ordering the beer. This product is designed for large customers; at first, we will be designed one product after that we will continue to make more products for large customers. It is intended for general use as it is used in big brewing companies, hotels and stores to keep the track of beer. The purpose of the product is to make available in widespread and broad for the customer.

