Discuss the state-of-the-art with respect to your product. What solutions currently exist, and in what form (academic research, enthusiast prototype, commercially available, etc)? Include references and citations as necessary \cite{Rubin2012}. If there are existing solutions, why won't they work for your customer (too expensive, not fast enough, not reliable enough, etc.). This section should occupy 1/2 - 1 full page, and should include at least 5 references to related work.

We want to design a more versatile system that can adapt to small companies and focus more on the adaptability of the software to the needs of the customer so that it can be used in different cases. There are a lot of  solutions for this kind of problem, most of the are commercial since managing inventories has always been a problem, both online and desktop applications are offered.

\textbf{Cin7} is the automated inventory management platform for brands growing their production, it is an online application that requires a monthly fee.
Cin7 integrates the entire product flow from the time it is in the warehouse until it leaves. It can help to run a warehouse much more smoothly since it has a great visibility at all the stages. No need to bother looking around for a product since the Cin7 has a very efficient tracking system.

\textbf{Pros:} The reporting is very well done. It offers a lot of features.

\textbf{Cons:} There is a learning curve, it is not very intuitive so you must learn to use it by reading the documentation.Has an outdated design and it is quite expensive.

\textbf{TradeGecko} is powerful inventory and order management software, it includes intelligent reports and forecasting, manufacturing, a customizable platform plus a mobile sales and inventory app on iPhone and iPad.

\textbf{Pros:} The software is smooth, integrates with the real world and requires minimal training. The inventory management component simplifies inventory management and provides us with all the information we need to manage inventory (no small task).

\textbf{Cons:} Smartphone app is limited. Browser-based software is somewhat slow requiring refreshes for up-to-date stock as well as pretty long loading times during navigation.

\textbf{Finale Inventory} is a cloud inventory software for Warehouse Management. Centralizes your inventory across multiple channels and warehouses. Stock changes made in inventory software gets updated instantly to all added channels.

\textbf{Pros:} Highly Customizable, nearly everything within the software can be customized to the way you want to view it on screen, printed as a report, for search, etc. Easy Copy Paste spreadsheet type updates.

\textbf{Cons:}Coming from a different software previously, there was a steep learning curve as you would expect. Figuring out how you want to customize your screen takes some time as there are just so many features. 
